CF Registry Analysis

### 2024-11-12 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
three models only

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
source(paste0(github_dir, "/shared-resources/Visualization/forest_plots.R"))
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
# Origin for survival analyses
og <- ymd("2003-01-01")
# Need to use a dataframe not a tibble
annual <- as.data.frame(annual)
# Formula for base model
xvars <- c(
  "age_group", "Gender", "Race", "Hispanicrace", "bmi_perc_cat", "MutClass",
  "A_IsOnEnzymes", "tube_feeding", "liver_disease", "ppFEV1_cat",
  "NumPulmExacerbation", "A_corticosteroids1"
)
y <- "Surv(time = as.numeric(tstart), time2 = as.numeric(tstop), event = as.numeric(CFRD) == 2)"
f <- as.formula(paste0(y, "~", paste0(xvars, collapse = "+")))
cox_res <- coxph(f, data = annual, cluster = eDWID)
# Forest plot and coefficients table
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_table(cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
# Diagnostics
test.ph <- data.frame(cox.zph(cox_res)$table)
test.ph <- test.ph[rownames(test.ph) != "GLOBAL", ]
# Find which variables technically violate PH assumption
time_varying <- rownames(test.ph)[test.ph$p < 0.05]
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry")
```

@@

```{r}
# Origin for survival analyses
og <- ymd("2003-01-01")
# Need to use a dataframe not a tibble
annual <- as.data.frame(annual)
# Formula for base model
xvars <- c(
  "age_group", "Gender", "Race", "Hispanicrace", "bmi_perc_cat", "MutClass",
  "A_IsOnEnzymes", "tube_feeding", "liver_disease", "ppFEV1_cat",
  "NumPulmExacerbation", "A_corticosteroids1"
)
y <- "Surv(time = as.numeric(tstart), time2 = as.numeric(tstop), event = as.numeric(CFRD) == 2)"
f <- as.formula(paste0(y, "~", paste0(xvars, collapse = "+")))
cox_res <- coxph(f, data = annual, cluster = eDWID)
# Forest plot and coefficients table
cox_res %>%
  tbl_regression(exponentiate = T)
ggcoef_table(cox_res,
  show_p_values = F, add_reference_rows = T, exponentiate = T,
  signif_stars = F, colour = F
)
# Diagnostics
test.ph <- data.frame(cox.zph(cox_res)$table)
test.ph <- test.ph[rownames(test.ph) != "GLOBAL", ]
# Find which variables technically violate PH assumption
time_varying <- rownames(test.ph)[test.ph$p < 0.05]
# Just split data by time period so we're only fitting 3 models
# "[2003,2009)", "[2009,2014)", "[2014,2019)"
annual$time_period <- cut(annual$ReviewYear,
  breaks = c(-Inf, 2009, 2014, Inf), right = F
)
era1 <- coxph(f, data = annual[as.numeric(annual$time_period) == 1, ], cluster = eDWID)
era2 <- coxph(f, data = annual[as.numeric(annual$time_period) == 2, ], cluster = eDWID)
era3 <- coxph(f, data = annual[as.numeric(annual$time_period) == 3, ], cluster = eDWID)
```
